---
title: "Case study"
output: github_document
always_allow_html: true
---


```{r setup, include = FALSE}

library(tidyverse)
library(p8105.datasets)
library(leaflet)

knitr::opts_chunk$set(
  fig.width = 6, 
  fig.asp = .6, 
  out.width = "90%"
)

theme_set(theme_minimal()+ theme(legend.position = "bottom")) 

options(
  ggplot2.continuous.color = "viridis", 
  ggplot2.continuous.fill = "viridis"
)


```


## Load the airbnb data 

```{r}

data("nyc_airbnb")

```

## Brainstorm some questions 

*What is the best Airbnb in Staten Island for < 100?
*What price range is popular in each borough? most rented?
*What apartment features are related to price?
*Cheapest room type in each neighborhood? 
*Hosts have higher ratings?

## Answer some questions

data cleaning

```{r}

nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(stars = review_scores_location/2)
  
```

```{r}

nyc_airbnb %>%
  count(neighbourhood_group, room_type) %>%
  pivot_wider(
    names_from = room_type, 
    values_from = n
  )

``` 

```{r}

nyc_airbnb %>%
  group_by(neighbourhood_group, room_type) %>%
  summarize(mean_price = mean(price))

```
```{r}

nyc_airbnb %>%
  filter(neighbourhood_group == "Manhattan") %>%
  count(neighbourhood)

```



```{r}

nyc_airbnb %>%
  filter(price < 1000, 
         neighbourhood_group == "Manhattan") %>%
  mutate(neighbourhood = fct_reorder(neighbourhood, price)) %>%
  ggplot(aes(x= neighbourhood, y = price)) + 
  geom_boxplot() +
  coord_flip()

```


```{r}

nyc_airbnb %>% 
  sample_n(1000) %>%
  ggplot(aes(x = lat, y = long, color = price)) + 
  geom_point()

```

## Create a leaflet map
```{r}

nyc_airbnb %>%
  sample_n(100) %>% 
  leaflet() %>%
  addProviderTiles(providers$CartoDB.Positron) %>%
  addCircleMarkers(~lat, ~long, radius = 1)
  

```





